\vspace*{4cm}
\begin{center}
    {\Huge\bfseries Abstract}
\end{center}
\vskip 1cm

\phantomsection
\addcontentsline{toc}{chapter}{Abstract}

The digital transformation of healthcare has led to the emergence of connected medical devices, electronic health records, remote monitoring platforms, and Artificial Intelligence-based decision-support systems. Although these technologies generate large amounts of heterogeneous data, many eHealth systems remain fragmented, static, and weakly personalized. Digital Twin technology offers a structured paradigm for addressing these limitations by connecting physical entities, processes, or patients with virtual representations that can be updated, analyzed, simulated, and used to support decisions.

This Master’s thesis presents a structured state-of-the-art study of Digital Twins for eHealth. It reviews eHealth foundations and analyzes the evolution of Digital Twin definitions from the classical three-dimensional physical--virtual model toward extended data- and service-centered approaches. It then studies maturity levels and healthcare applications before developing two complementary states of the art. The first examines Digital Twins in eHealth and healthcare, including patient-specific twins, organ and device twins, hospital-process twins, public-health twins, Artificial Intelligence-enabled services, interoperability, privacy, ethics, governance, and validation. The second focuses on cardiovascular Digital Twins as a representative clinical deep-dive, covering electrophysiology, hemodynamics, heart-failure models, patient-specific calibration, hybrid AI--mechanistic approaches, population-scale cardiac twins, and validation challenges.

The thesis includes a comparison of representative Digital Twin definitions, two comparative landscape tables, and several academic synthesis figures that clarify definition streams, AI roles, eHealth Digital Twin categories, cardiovascular Digital Twin categories, maturity evidence, and the transition from the reviewed literature to the CardioTwin PFE. The work derives a conceptual multi-layer architecture and explicit design implications for CardioTwin while preserving the general eHealth scope of the Master’s study. CardioTwin is introduced only as a practical cardiovascular continuation that will require implementation, evaluation, and future clinical validation.

\textbf{Keywords:} Digital Twin, eHealth, Digital Health, Healthcare, Cardiovascular Digital Twin, Artificial Intelligence, Simulation, Interoperability, Clinical Decision Support, CardioTwin.

\clearpage
