\chapter{General Introduction}

\section{Context}
Healthcare systems are increasingly supported by digital technologies such as connected medical devices, electronic health records, telemedicine platforms, mobile health applications, and artificial intelligence-based analytics. This evolution has contributed to the emergence of eHealth, a broad domain that aims to improve healthcare delivery, monitoring, prevention, diagnosis, and patient engagement through information and communication technologies.

At the same time, healthcare data are becoming more heterogeneous and continuous. A patient may generate information through clinical consultations, laboratory tests, medical imaging, wearable devices, mobile applications, and hospital information systems. The challenge is no longer only to collect data, but also to transform these data into meaningful, reliable, and actionable knowledge for healthcare professionals and patients.

Digital Twin technology has recently gained attention as a promising paradigm for representing physical entities and processes through dynamic virtual counterparts. In healthcare, a Digital Twin may support the representation of a patient, a medical device, a hospital service, a clinical workflow, or even a population-level process. The objective is to connect real-world data with virtual models in order to monitor current states, simulate possible futures, and support decision-making.

\section{Problem Statement}
Despite the progress of eHealth systems, several limitations remain. First, medical data are often distributed across multiple systems and formats, which makes integration and interoperability difficult. Second, many digital health applications provide static analysis based on isolated measurements rather than dynamic representations that evolve with the real-world situation. Third, decision support systems frequently rely on general population models and may not sufficiently account for individual variability, contextual information, and temporal evolution.

These limitations raise the following central problem:

\begin{quote}
How can Digital Twin technology be used as a conceptual and architectural foundation for building eHealth systems that are more dynamic, interoperable, personalized, and capable of supporting monitoring, simulation, and decision-making?
\end{quote}

\section{Research Motivation}
The motivation of this thesis comes from the need to move from fragmented eHealth applications toward integrated and intelligent healthcare ecosystems. A Digital Twin-based approach can provide a structured way to combine real-world data, virtual representation, simulation, artificial intelligence, and decision services. This is particularly relevant in healthcare because clinical decisions depend not only on current measurements, but also on patient history, context, uncertainty, and possible future trajectories.

While this thesis examines Digital Twins for eHealth in a general healthcare context, cardiovascular Digital Twins are used as a representative clinical deep-dive. This domain combines multimodal biosignals, imaging, hemodynamic measurements, longitudinal monitoring, and patient-specific physiological modeling, making it suitable for analyzing the transition from conceptual Digital Twin architectures to clinically oriented implementations~\cite{coorey2022health,corralacero2020digital}. This running case also establishes the theoretical basis for the cardiovascular specialization introduced in the PFE.

\section{Objectives}
The main objective of this thesis is to study the state of the art of Digital Twin technology in eHealth and to derive the conceptual, architectural, and evaluation principles required for trustworthy eHealth Digital Twin systems. The specific objectives are:

\begin{itemize}[leftmargin=*]
    \item to study the evolution, definitions, components, and maturity levels of Digital Twins;
    \item to review the foundations of eHealth and digital health systems in which Digital Twin principles may be applied;
    \item to analyze the use of Digital Twins in healthcare from a general eHealth perspective;
    \item to study major healthcare application domains, including personalized medicine, remote monitoring, hospital processes, public health, and cardiovascular applications;
    \item to use cardiovascular Digital Twins as a representative clinical deep-dive for multimodal and patient-specific modeling;
    \item to compare existing architectures, technologies, applications, and limitations;
    \item to identify major challenges related to interoperability, security, privacy, ethics, and validation;
    \item to synthesize a multi-layer eHealth Digital Twin architecture and evaluation framework from the reviewed literature;
    \item to introduce CardioTwin as a practical cardiovascular continuation for the final PFE project.
\end{itemize}

\section{Contributions}
The main contributions of this thesis are:

\begin{itemize}[leftmargin=*]
    \item a structured conceptual review of Digital Twin definitions, components, maturity levels, and enabling technologies;
    \item a classification of healthcare Digital Twin applications from a general perspective;
    \item a representative cardiovascular deep-dive connecting biosignals, hemodynamics, imaging, physiological modeling, and longitudinal monitoring;
    \item a comparative study of selected research papers and architectures;
    \item architecture and evaluation findings derived from the comparative synthesis of the literature;
    \item a discussion of implementation challenges, research gaps, and future research directions;
    \item a transition toward the CardioTwin PFE as a practical cardiovascular specialization of the general findings.
\end{itemize}

\section{Thesis Outline}
This thesis is organized into four main parts. Part I contains the general introduction and presents the research context, problem statement, objectives, and contributions. Part II provides the background: Chapter 2 introduces Digital Twin fundamentals, Chapter 3 presents eHealth and digital-health foundations, and Chapter 4 examines how Digital Twin concepts are applied in healthcare and eHealth, including cardiovascular Digital Twins as a representative clinical deep-dive. Part III presents the state of the art: Chapter 5 defines the structured literature review methodology, while Chapter 6 compares selected studies, synthesizes the main conceptual and architectural findings, derives a multi-layer eHealth Digital Twin architecture, and identifies the remaining research gaps. Part IV contains the final chapter, which concludes the Master study and introduces the proposed PFE method through CardioTwin, a cardiovascular Digital Twin specialization.

\clearpage
